Architectures and Open pNets

### 2018-11-30 2018-Arch-pNets/arch-pNets.tex
listing brut du calcul des OT

>>>>

\subsection{Full results of the use-case}
\label{secn:full-results}

\subsubsection{Output of the open-automaton construction}
The standard pretty-print of OTs by the tool include the transitions of the pLTSs (controllers). This is not a full ``proof-carrying code'', but it allows for a better understanding of the construction of each OT.

\begin{verbatim}
INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
INFO  BIPArchFailureTimerMax_LTF3 -
        {t0---init-->t1, s0---init-->s1},   {},   
        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=ini
t))/\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
    OT ------------------------------------------------------------
        <t0_s0>-----:ra:1:5----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],
   {t := (t+1), z := z1}
    OT ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra
:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail
(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_SV
0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t+1
), z := z1}
    OT ------------------------------------------------------------
        <t1_s1>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT ------------------------------------------------------------
        <t1_s1>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],   {t := (t+1)}
    OT ------------------------------------------------------------
        <t1_s1>-----:ra:1:3----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:r
a:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fa
il(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_
SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t
+1), z := z1}
    OT ------------------------------------------------------------
        <t1_s2>-----:ra:1:1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cance
l(b1:sva_SV1:1:2)))/\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva_SV1
:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {t := 0, z := TopInt}
    OT ------------------------------------------------------------
        <t1_s2>-----:ra:1:2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],   {t := (t+1)}
    OT ------------------------------------------------------------
        <t1_s2>-----:ra:1:3----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:r
a:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fa
il(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_
SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t
+1), z := z1}
    OT ------------------------------------------------------------
        <t1_s3>-----:ra:1:1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
    OT ------------------------------------------------------------
        <t1_s3>-----:ra:1:2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {s3---reset-->s1},   {---:hb_E:116:8-->},   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3
=:ra:1:4))],   {}
    OT ------------------------------------------------------------
        <t1_s3>-----:ra:1:4----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
FailureTimerArchi
--------------------
SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0, ((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))
SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
SV2 SVs: <timeout, timeout, _, ask>-->alpha2
SV3 SVs: <_, reset, _, reset>-->alpha3
SV4 SVs: <init, init, _, _>-->alpha4
pLTS: Timer
- Transition: t0---init-->t1, { t := 0 z := TopInt}
- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
- Transition: t1---cancel(false)-->t1, {}
- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
- Variable: t, State: t1, Value(s) = 0,0,(t+1),
- Variable: z, State: t1, Value(s) = TopInt,z1,
pLTS: Failure
- Transition: s0---init-->s1, { zone := minZone,maxZone}
- Transition: s1---timeout-->s1, {}
- Transition: s1---resume(false)-->s1, {}
- Transition: s1---fail(zone, false)-->s1, {}
- Transition: s1---fail(zone, true)-->s2, {}
- Transition: s2---fail(zone, false)-->s2, {}
- Transition: s2---resume(false)-->s2, {}
- Transition: s2---resume(true)-->s1, {}
- Transition: s2---timeout-->s3, {}
- Transition: s3---fail(zone, false)-->s3, {}
- Transition: s3---resume(false)-->s3, {}
- Transition: s3---reset-->s1, {}
- Variable: zone, State: s1, Value(s) = minZone,maxZone,
Holes: B
Holes: E
\end{verbatim}
